### 2021-05-25 article/article.tex
update

{\renewcommand{\arraystretch}{1.3}
 \begin{table}
   \begin{center}
   \begin{tabular}{lcccccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{6}{c}{IceCube}  \\
      $\epsilon_{\mu\tau}$  &   [-0.01, 0.009] &  [-0.015, 0.014] &  [-0.013, 0.012] &  [-0.019, 0.018] &  [-0.015, 0.014] &  [-0.022, 0.021] \\\\
      & \multicolumn{6}{c}{DeepCore}\\ [0.3em]
      $\epsilon_{\tau\tau}$ &   [-0.04, 0.063] &               [] &   [-0.04, 0.063] &               [] &   [-0.04, 0.063] &               [] \\
      $\epsilon_{\mu\tau}$  &  [-0.023, 0.007] &          [0.023] &  [-0.023, 0.007] &          [0.023] &  [-0.023, 0.007] &          [0.023] \\
      $\epsilon_{e\mu}$     &  [-0.107, 0.113] &   [-0.198, 0.19] &  [-0.107, 0.113] &   [-0.198, 0.19] &  [-0.107, 0.113] &   [-0.198, 0.19] \\
      $\epsilon_{e\tau}$    &  [-0.111, 0.212] &     [-0.26, 0.3] &  [-0.111, 0.212] &     [-0.26, 0.3] &  [-0.111, 0.212] &     [-0.26, 0.3] \\\\
      &\multicolumn{6}{c}{IceCube + DeepCore}\\
      $\epsilon_{\mu\tau}$  &    [-0.027, 0.0] &          [0.016] &    [-0.027, 0.0] &          [0.016] &    [-0.027, 0.0] &          [0.016] \\
      \hline
      \hline
   \end{tabular}
   \end{center}
   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
\end{table}
\begin{table}
   \begin{tabular}{lcccccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{6}{c}{PINGU} \\
      $\epsilon_{\tau\tau}$ &  [-0.033, 0.057] &         [-0.048] &  [-0.034, 0.059] &         [-0.051] &  [-0.037, 0.062] &         [-0.055] \\
      $\epsilon_{\mu\tau}$  &  [-0.007, 0.007] &  [-0.011, 0.013] &  [-0.007, 0.008] &  [-0.012, 0.014] &  [-0.008, 0.009] &  [-0.014, 0.016] \\
      $\epsilon_{e\mu}$     &  [-0.062, 0.057] &  [-0.122, 0.104] &  [-0.081, 0.067] &   [-0.162, 0.12] &   [-0.106, 0.08] &  [-0.199, 0.141] \\
      $\epsilon_{e\tau}$    &   [-0.07, 0.077] &   [-0.12, 0.133] &  [-0.086, 0.089] &   [-0.15, 0.148] &  [-0.107, 0.102] &  [-0.182, 0.164] \\\\
      & \multicolumn{6}{c}{DeepCore + PINGU} \\
      $\epsilon_{\tau\tau}$ &   [-0.033, 0.05] &  [-0.048, 0.065] &  [-0.033, 0.052] &   [-0.05, 0.067] &  [-0.035, 0.051] &  [-0.052, 0.068] \\
      $\epsilon_{\mu\tau}$  &  [-0.007, 0.006] &  [-0.011, 0.012] &  [-0.007, 0.006] &  [-0.012, 0.012] &  [-0.004, 0.011] &   [-0.01, 0.017] \\
      $\epsilon_{e\mu}$     &  [-0.057, 0.052] &  [-0.107, 0.095] &   [-0.067, 0.06] &  [-0.127, 0.107] &  [-0.097, 0.056] &   [-0.165, 0.11] \\
      $\epsilon_{e\tau}$    &  [-0.063, 0.075] &  [-0.113, 0.128] &  [-0.074, 0.086] &  [-0.136, 0.142] &  [-0.115, 0.065] &  [-0.184, 0.131] \\\\
      & \multicolumn{6}{c}{IceCube + DeepCore + PINGU}  \\
      $\epsilon_{\mu\tau}$  &  [-0.009, 0.004] &  [-0.013, 0.009] &  [-0.009, 0.004] &   [-0.014, 0.01] &  [-0.008, 0.007] &  [-0.012, 0.013] \\
      \hline
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}

>>>>

{\renewcommand{\arraystretch}{1.3}
 \begin{table}
   \begin{center}
   \begin{tabular}{lcccccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{6}{c}{IceCube}  \\
      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\\\
      & \multicolumn{6}{c}{DeepCore}\\ [0.3em]
      $\ett$ &  [-0.044, 0.051] &  [-0.062, 0.069] &  [-0.046, 0.054] &         [-0.065] &  [-0.049, 0.057] &          [-0.07] \\
      $\emt$ &  [-0.008, 0.009] &  [-0.014, 0.017] &   [-0.009, 0.01] &  [-0.015, 0.018] &   [-0.01, 0.011] &   [-0.017, 0.02] \\
      $\eem$ &  [-0.079, 0.081] &   [-0.16, 0.14] &  [-0.11, 0.094] &  [-0.20, 0.16] &   [-0.14, 0.11] &   [-0.23, 0.18] \\
      $\eet$ &  [-0.079, 0.098] &  [-0.15, 0.16] &   [-0.10, 0.11] &  [-0.19, 0.18] &  [-0.13, 0.13] &  [-0.23, 0.12] \\\\
      &\multicolumn{6}{c}{IceCube + DeepCore}\\
      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
      \hline
      \hline
   \end{tabular}
   \end{center}
   \caption{IceCube and DeepCore results from the $\Delta \chi^2$ in Fig.~\ref{fig:IC_3D}. Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:IC_DC_results}
\end{table}
\begin{table}
   \begin{tabular}{lcccccc}
      \hline \hline
      Parameter & Best 90\% CL & Best $3\sigma$& Baseline 90\% CL & Baseline $3\sigma$ & Worst 90\% CL & Worst $3\sigma$\\
      \hline & \multicolumn{6}{c}{PINGU} \\
      $\ett$ &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] &  [-0.054, 0.067] &               [] \\
      $\emt$ &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] &  [-0.029, 0.007] &          [0.026] \\
      $\eem$ &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] &  [-0.12, 0.15] &  [-0.23, 0.24] \\
      $\eet$ &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] &   [-0.084, 0.15] &  [-0.19, 0.21] \\\\
      & \multicolumn{6}{c}{DeepCore + PINGU} \\
      $\ett$ &  [-0.036, 0.046] &  [-0.056, 0.064] &  [-0.038, 0.048] &  [-0.058, 0.067] &   [-0.039, 0.05] &          [-0.06] \\
      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
      $\eem$ &   [-0.06, 0.077] &  [-0.126, 0.127] &  [-0.071, 0.086] &  [-0.149, 0.141] &  [-0.082, 0.097] &  [-0.17, 0.16] \\
      $\eet$ &  [-0.052, 0.095] &  [-0.112, 0.144] &  [-0.061, 0.103] &  [-0.131, 0.155] &  [-0.067, 0.11] &  [-0.15, 0.17] \\\\
      & \multicolumn{6}{c}{IceCube + DeepCore + PINGU}  \\
      $\emt$ &  [-0.009, 0.006] &  [-0.015, 0.013] &   [-0.01, 0.006] &  [-0.016, 0.014] &  [-0.011, 0.007] &  [-0.017, 0.015] \\
      \hline
      \hline
   \end{tabular}
   \caption{PINGU and joint results from the $\Delta \chi^2$ in Fig.~\ref{fig:3D_NO}. Best, baseline, and worst refer to 
   the systematic uncertainty scenarios considered as in Table~\ref{table:syst_errors}.}\label{table:PINGU_joint_results}
\end{table}
